Patient-Specific Neural Field Modeling from Micro-Electrode Data

### 2010-07-26 ltx/data_paper/DataPaper.tex
added missing paramater in EM (Dean comment)

&=\mathbf E_{\boldsymbol (\theta',\xi')}\left[\sum_{t=1}^{T}\ln p(\mathbf y_t|\mathbf x_t)+\sum_{t=1}^{T}\ln p(\mathbf x_t|\mathbf x_{t-1};\boldsymbol \theta)+\sum_{t=1}^{T}\ln p(\mathbf x_0)\right],

@@

\dean{there is a parameter missing here..} where $ \mathbf E_{\boldsymbol (\theta',\xi')}$ denotes expectation taken with respect to the distribution $p(\mathbf X | \mathbf Y;\boldsymbol \theta',\xi') $ where $\boldsymbol \theta'$ and $\xi'$are the current parameter estimates. It should be noted that

>>>>

&=\mathbf E_{\boldsymbol (\theta',\xi')}\left[\sum_{t=1}^{T}\ln p(\mathbf y_t|\mathbf x_t)+\sum_{t=1}^{T}\ln p(\mathbf x_t|\mathbf x_{t-1};\boldsymbol \theta, \xi)+\sum_{t=1}^{T}\ln p(\mathbf x_0)\right],

@@

where $ \mathbf E_{\boldsymbol (\theta',\xi')}$ denotes expectation taken with respect to the distribution $p(\mathbf X | \mathbf Y;\boldsymbol \theta',\xi') $ where $\boldsymbol \theta'$ and $\xi'$are the current parameter estimates. It should be noted that
